### 2021-02-18 architecture.tex
Improve architecture overview

This section describes a structure of a symbol precedence recommender.
When presented with a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
the recommender generates a precedence $\pi^*$ of symbols $\Sigma$.

@@

\begin{figure}[ht]
\caption{Architecture overview}
\centering
\digraph[scale=0.4]{ArchitectureOverview}{
graph [splines=ortho];
node [shape=box, fontsize=20];
edge [fontsize=20];

Problem [label="CNF problem"];
GCN [style=rounded, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=rounded, label="MLP"];
SymbolCost [label="Symbol costs"];
Sort [style=rounded, label="Sort"];
Precedence [label="Output precedence"];

Problem -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;

>>>>

\subsection{System overview}

The precedence recommender is a system that takes
a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
and produces a precedence over the symbols $\Sigma$ as the output.

The architecture is designed so that the recommender can be trained
on the results of solver executions with random precedences.
The recommender is parameterized by weight tensors
whose values can be trained by gradient descent.
\todo{Ensure we have defined this.}
The goal of the training is to find parameter values
such that the recommender produces precedences
that are likely to yield a successful proof in few iterations of the saturation loop.

The recommender consists of modules that perform specific subtasks (see \cref{fig:architecture}):
\begin{enumerate}
\item Graphifier converts the input \gls{cnf} problem into a problem graph.
\item \gls{gcn} converts a problem graph into symbol embeddings.
The \gls{gcn} contains one or more convolution layers.
\item Projection converts the symbol embeddings into a vector of symbol costs.
\item Sorting converts the symbol costs into a symbol precedence.
It is only used in generating mode.
\item Loss function converts the symbol costs and a pair of precedences into a loss value.
It is only used in training mode.
\end{enumerate}

\begin{figure}[h]
\caption{Recommender architecture overview.
When recommending a precedence, the input is problem $P$ and the output is precedence $\pi^*$.
When training on an example, the input is problem $P$ and precedences $\pi$ and $\rho$,
and the output is the loss value.}
\label{fig:architecture}
\centering
\digraph[scale=0.4]{ArchitectureOverview}{
graph [splines=ortho,ranksep=0.2];
node [shape=box, fontsize=20];
edge [fontsize=20];

Problem [label="CNF problem P"];
Graphifier [style=rounded, label="Graphifier"];
g [label="Graph"];
GCN [style=rounded, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=rounded, label="Projection"];
SymbolCost [label="Symbol costs"];
Sort [style=rounded, label="Sort"];
Precedence [label=<Output precedence &pi;*>];

Problem -> Graphifier -> g -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;

@@
